Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2021-06-28 manuscript.tex
Make more precise and remove white-space before \n [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/429775d8cac323cb2f3dcf877f9bf725e7a547ab.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/429775d8cac323cb2f3dcf877f9bf725e7a547ab/checks
https://github.com/habi/acinar-analysis-manuscript/runs/979560659

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been submited to \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...b00473f3d253b202af4827cb50f0be832208e927}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/b00473f3d253b202af4827cb50f0be832208e927/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/b00473f3d253b202af4827cb50f0be832208e927}{habi/acinar-analysis-manuscript@b00473f}
on June 17, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(b00473f)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(b00473f)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

@@

\hypertarget{total-number-of-alveoli-per-lung}{%
\subsubsection{Total number of alveoli per lung}\label{total-number-of-alveoli-per-lung}}

@@

We can easily estimate the total number of acini during lung development from our data.
The limitations of this study are mainly twofold: a) due to technical reasons (i.e.~available beamtime and limitations of the setup we could not image the entire lung and b) lung location (i.e.~lower medial tip of the right lobe).
However, our sample is more than suitable for the drawn conclusions because it was previously shown that the right lower lobe is a valid sample for the entire lung {[}\protect\hyperlink{ref-14OP85b2F}{10}{]} and that information drawn from one lobe is representative of the whole lung {[}\protect\hyperlink{ref-I9TmP6IU}{45}{]}.
Furthermore, based on stereological data, Zeltner et al.~{[}\protect\hyperlink{ref-I9TmP6IU}{45}{]} were able to show that the lung parenchyma is rather homogeneous.
Looking at individual acini, Kizhakke Puliyakote et al.~{[}\protect\hyperlink{ref-RGBeCf8v}{22}{]} observed that the peripheral, pleura facing acini possess an acinar volume which is two thirds larger than the volume of the central ones.
However, they did not report additional regional differences, for example between acini located cranially and caudally.
Own preliminary data point to the same result.
We imaged an entire rat lung \emph{in situ} immediately post mortem using high-resolution synchrotron radiation based X-ray tomographic microscopy {[}\protect\hyperlink{ref-Zv1XcgAO}{46}{]}.
A first analysis of regional difference shows similar results as mentioned above.

\hypertarget{acinus-volumes}{%
\subsubsection{Acinus volumes}\label{acinus-volumes}}

@@

Based on the acinar and parenchymal volume we calculated the number of acini and were able to verify the previously reported results to lie within our margin of error at days 4 and 60 (Barré et al.: 6236~±~497~acini and 5612~±~547~acini, respectively).
As shown in figure~\ref{fig:07}, our values ± their standard deviation are overlapping the previously found values, even though we generally see a trend that the number of acini seems to decrease during lung development.
This might be due to fusing of several acini to one or simply because we missed some acini in the analysis of the large datasets.

@@

\hypertarget{total-alveolar-number}{%
\subsubsection{Total alveolar number}\label{total-alveolar-number}}

@@

\hypertarget{volumes-of-individual-alveoli}{%
\subsubsection{Volumes of individual alveoli}\label{volumes-of-individual-alveoli}}

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been submited to \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...429775d8cac323cb2f3dcf877f9bf725e7a547ab}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/429775d8cac323cb2f3dcf877f9bf725e7a547ab/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/429775d8cac323cb2f3dcf877f9bf725e7a547ab}{habi/acinar-analysis-manuscript@429775d}
on June 28, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(429775d)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(429775d)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

@@

\hypertarget{number-of-alveoli-per-lung}{%
\subsubsection{Number of alveoli per lung}\label{number-of-alveoli-per-lung}}

@@

We can easily estimate the total number of acini during lung development from our data.
The limitations of this study are mainly twofold: a) due to technical reasons (i.e.~available beamtime and limitations of the setup) we were not able to image the entire lung and b) lung location (i.e.~lower medial tip of the right lobe).
However, our sample is more than suitable for the drawn conclusions because it was previously shown that the right lower lobe is a valid sample for the entire lung {[}\protect\hyperlink{ref-14OP85b2F}{10}{]} and that information drawn from one lobe is representative of the whole lung {[}\protect\hyperlink{ref-I9TmP6IU}{45}{]}.
Furthermore, based on stereological data, Zeltner et al.~{[}\protect\hyperlink{ref-I9TmP6IU}{45}{]} were able to show that the lung parenchyma is rather homogeneous.
Looking at individual acini, Kizhakke Puliyakote et al.~{[}\protect\hyperlink{ref-RGBeCf8v}{22}{]} observed that the peripheral, pleura facing acini possess an acinar volume which is two thirds larger than the volume of the central ones.
However, they did not report additional regional differences, for example between acini located cranially and caudally.
Own preliminary data point to the same result.
We imaged an entire rat lung \emph{in situ} immediately post mortem using high-resolution synchrotron radiation based X-ray tomographic microscopy {[}\protect\hyperlink{ref-Zv1XcgAO}{46}{]}.
A first analysis of regional difference shows similar results as mentioned above.

\hypertarget{acinus-volume-1}{%
\subsubsection{Acinus volume}\label{acinus-volume-1}}

@@

Based on the acinar and parenchymal volume we calculated the number of acini and were able to verify the previously reported results to lie within our margin of error at days 4 and 60 (Barré et al.: 6236~±~497~acini and 5612~±~547~acini, respectively).
As shown in figure~\ref{fig:07}, our values ± standard deviation are overlapping the previously found values, even though we generally see a trend that the number of acini seems to decrease during lung development.
This might be due to fusing of several acini to one or simply because we missed acini when performing the analysis of the large datasets.

@@

\hypertarget{number-of-alveoli-per-lung-1}{%
\subsubsection{Number of alveoli per lung}\label{number-of-alveoli-per-lung-1}}

@@

\hypertarget{volume-of-individual-alveoli-1}{%
\subsubsection{Volume of individual alveoli}\label{volume-of-individual-alveoli-1}}
